---
editor_options: 
  markdown: 
    wrap: 72
---

# Set environment and import data

```{r}
rm(list=ls())
library(reshape2)
library("ggplot2")
library(patchwork)
library(gridExtra)
```

reading data

```{r}
wine=readRDS(file="./data/wine.Rda")
wine[431:440, ]
# saving the dataframe in a png file for the report
png("pictures/example_covariates.svg", height = 50*nrow(wine[431,]), width = 200*ncol(wine))
#grid.table(correlated_covariates)
#dev.off()
```

All the columns are continuous, a part from the quality one. Free sulfur
dioxide and Total sulfur dioxide are continuous covariates even thought
by the values it seems they are discrete. They are continuous since they
are measures (mg/L) [Conventional Measurements of Sulfur Dioxide (SO2)
in Red Wine Overestimate SO2 Antimicrobial Activity \~
<https://www.extension.iastate.edu/wine/wp-content/uploads/2019/04/conventional_so2_overestimates_in_red_wine_ajev_2018.pdf>].
Furthermore, with more attention we can find continuous value at rows
433 and 439.

Here we import all our custom functions

```{r}
source("utils_functions.R")
```

# Data analysis

Plotting the histogram distributions for each column of the dataframe
wine.

```{r}
# settings
hist_plts <- ggplot_hist_data(wine)
hist_plts
#ggsave("pictures/histograms.png", plot = hist_plts)
```

What we notice is the presence of long tails for most of the columns,
this suggests the presence of outliers. A part from the alcohol,
sulphates, total.sulfur.dioxide distributions, if we remove the tails
data are symmetrically distributed. Quality data are highly concentrated
in the range of values (5- 7): since the quality is our target value, we
may encounter some issues during the predictions as the data are
unbalanced.

## Correlation analysis

Plotting correlation matrix using Pearson index.

```{r}
cor_plt <- plot_correlation(wine, "Pearson\n correlation")
cor_plt
# saving the correlation plot as a png picture
#ggsave("pictures/pearson.png", plot = cor_plt)

```

When performing predictions of quality we should care about the
correlation among the covariates. If two covariates are highly
correlated we may encounter strange results, so we should also consider
to keep only low correlated covariates.

Find highly correlated covariates (absolute value of Pearson index
greater than or equal to 0.5) here.

```{r}
melted_wine = melt(cor(wine))
correlated_covariates = find_competitive_covariates(melted_wine, 0.5, "quality")
correlated_covariates
# saving the dataframe in a png file for the report
#png("pictures/competitive_covariates.png", height = 50*nrow(correlated_covariates), width = 200*ncol(correlated_covariates))
#grid.table(correlated_covariates)
#dev.off()
```

Here I am looking for the covariates that seems to be more significant
according to the Pearson coefficient.

```{r}
correlation_with_quality = tail(melted_wine, n=12)
correlation_with_quality["value"] = abs(correlation_with_quality["value"])
correlation_with_quality = correlation_with_quality[order(correlation_with_quality$value, decreasing = TRUE),]
correlation_with_quality

# saving the dataframe in a png file for the report
#png("pictures/correlation_score_df.png", height = 50*nrow(correlation_with_quality), width = 200*ncol(correlation_with_quality))
#grid.table(correlation_with_quality)
#dev.off()
```

Considerations: the parameters are sorted by importance. We may expect
to keep the parameters with the highest correlation index with quality
while performing feature selection.

From the results above we can perform a prior feature selection. Given a
pair of highly correlated covariates I want to discard the less
significant.

Note: here I am not doing a feature selection with the goal of finding
the most significant features (this will be done with the right choice
of the prior) but I am just discarding in a greedy way features that may
lead to problems when training the model.

In this case we may consider to remove density and free.sulfur.dioxide

```{r}
to_remove <- c("density", "free.sulfur.dioxide")
filtered_wine <- wine[, ! names(wine) %in% to_remove, drop=F]
filtered_wine
```

```{r}
plot_correlation(filtered_wine, "Pearson\n correlation")
```

## Managing outliers

```{r}
box_plots <- get_box_plots_wine(wine)
box_plots
#ggsave("pictures/box_plots.png", plot = box_plots)
```

Find outliers in the original dataset.

```{r}
wine_m = remove_outliers(wine)
print(nrow(wine_m))
```

Find outliers in the filtered dataset.

```{r}
boxplot(filtered_wine, las=3,main="Covariates boxplot",cex.axis=0.75)
```

```{r}
wine_f_m = remove_outliers(filtered_wine)
nrow(wine_f_m)
```

From the quality of the histogram we can notice how the quality has high
mass on the values 5-6 and has just few values near 0 and 10 (the
extremes). We want to understand if the outliers are somehow connected
to very poor/good wines. If we have just few samples for bad/good wines,
one may think the features that characterize them might be the outliers
of the dataset. For this purpose we plot the estimated densities of the
dataset without outliers and the quality density of the outliers.

```{r}
outliers = keep_outliers(wine)
cleaned = remove_outliers(wine)
```

```{r}
c1 = red_ex
c2 = light_blue_ex

plt_outliers <- ggplot() + 
  geom_histogram(data=outliers, aes(x=quality, y=..density..), bins=10, color=c1, fill=c1, alpha=0.5, center=0,binwidth = 1) +
  geom_histogram(data=cleaned, aes(x=quality, y=..density..), bins=10, color=c2, fill=c2, alpha=0.5, center=0,binwidth = 1) +
  scale_x_continuous(breaks=c(0:10))

plt_outliers

#ggsave("pictures/outliers_vs_non.png", plot = plt_outliers)
```

From the histograms we can notice how the quality distributions for both
sets are comparable, thus we can not say anything about the outliers.

```{r}
# set these values to decide which outliers to keep
up=TRUE
down=FALSE


name= colnames(wine)[1] 
no_out = handle_outlier(wine, name, remove=TRUE, up=up, down=down)
yes_out = handle_outlier(wine, name, remove=FALSE, up=up, down=down)

plt_outliers <- ggplot() + 
  geom_histogram(data=yes_out, aes(x=quality, y=..density..), bins=10, color=red_ex, fill=red_ex, alpha=0.5, center=0,binwidth = 1) +
  geom_histogram(data=no_out, aes(x=quality, y=..density..), bins=10, color=light_blue_ex, fill=light_blue_ex, alpha=0.5, center=0,binwidth = 1) +
  scale_x_continuous(breaks=c(0:10), name=paste("quality", name))


for (i in 2:(ncol(wine)) - 1){
  name= colnames(wine)[i] 
  no_out = handle_outlier(wine, name, remove=TRUE, up=up, down=down)
  yes_out = handle_outlier(wine, name, remove=FALSE, up=up, down=down)
  if (nrow(no_out) != 0 & nrow(yes_out) != 0){
      plt_outliers <- plt_outliers + ggplot() + 
    geom_histogram(data=yes_out, aes(x=quality, y=..density..), bins=10, color=red_ex, fill=red_ex, alpha=0.5, center=0,binwidth = 1) +
    geom_histogram(data=no_out, aes(x=quality, y=..density..), bins=10, color=light_blue_ex, fill=light_blue_ex, alpha=0.5, center=0,binwidth = 1) +
    scale_x_continuous(breaks=c(0:10), name=paste("quality", name))
  }
}
plt = plt_outliers + plot_layout(ncol = 3)
plt
#ggsave("pictures/outliers_distributionsUP.png", plot=plt)
```

What happens if we scale the dataframe

```{r}
df.scaled <- as.data.frame(scale(cleaned))
summary(df.scaled)
```

```{r}
ggplot_hist_data(df.scaled)
```
