Load libraries and data:
```{r}
rm(list=ls())
library("ggplot2")
library(patchwork)
library(rjags)
library(coda)
source("utils_functions.R")

wine <- readRDS(file="./data/wine.Rda")
summary(wine)
```
Define labels and features, scale features:
```{r}
# Define outcome and design matrix (omit NA value)
X <- na.omit(as.matrix(wine[,1:(dim(wine)[2]-1)]))
Y <- na.omit(as.vector(wine$quality))

# standardize matrix
X <- scale(X)

# Get dimensions
N <- dim(X)[1]
p <- dim(X)[2]
```
$$
\newcommand{\iid}{\stackrel{\small\mathrm{iid}}{\sim}}
\begin{align*}
  y_j \mid p_j &\ind B(10, p_j) \\[5pt]
  p_j &\ind \Phi(\beta_0 + x_{\,j}^{\,T}\beta) \\[5pt]
  \beta_j \mid \gamma_j &\ind (1-\gamma_j)\,\delta_{\{0\}} + \gamma_j\,\mathcal{N}\left(0, \sigma^2_{\beta_j}\right) \\[5pt]
  \gamma_j \mid \theta_j &\ind \mathcal{B}e\left(\theta_j\right) \\[5pt]
  \theta_{j} &\iid \pi\left(\theta_j\right)
\end{align*}
$$
Define the JAGS model:
```{r}
cat(
  "
  model {
    # Likelihood 
    for (i in 1:N) {
    	Y[i] ~ dbin(phi(beta0 + X[i,] %*% beta[]), 10)
    } 
  
    # Tracing the visited model
    for (j in 1:p) {
    	TempIndicator[j] <- g[j]*pow(2, j) 
    }
    mdl <- 1 + sum(TempIndicator[]) # model index in binary coding 
  
    # Priors
    beta0 ~ dnorm(0, 0.01)
  
    for(j in 1:p) {
    	tprior[j] <- 1 / var_beta[j]
    	bprior[j] <- 0
    }
  
    for(j in 1:p) {
    	beta_temp[j] ~ dnorm(bprior[j], tprior[j])
    	g[j] ~ dbern(theta[j])
    	theta[j] ~ dunif(0,1)
    	beta[j] <- g[j] * beta_temp[j]	
    }
  }
  "
, file = "models/spikeslab_bin.bug")

# Data to pass to JAGS
data_JAGS <- list(N = N, p = p, Y = Y, X = as.matrix(X), var_beta = rep(1, p))

# A list of initial value for the MCMC algorithm 
inits = function() {
  list(beta0 = 0.0, beta_temp = rep(0,p), g = rep(0,p), theta = rep(0.5, p),
       .RNG.seed = 321, .RNG.name = 'base::Wichmann-Hill') 
}

# Compile model (+ adaptation)
model <- jags.model("models/spikeslab_bin.bug", data = data_JAGS,
                    n.adapt = 1000, inits = inits, n.chains = 2) 
```
Burn in:
```{r}
# if we want to perform a larger burn in with not adaptation.
cat("  Updating...\n")
update(model,n.iter=1000)
```
Run chain:
```{r}
# Posterior parameters JAGS has to track
param <- c("beta0", "beta", "g", "mdl", "beta_temp")

# Number of iterations & thinning
nit <- 100000
thin <-100

# Sampling (this may take a while)
cat("  Sampling...\n")
output <- coda.samples(model = model,
                       variable.names = param,
                       n.iter = nit,
                       thin = thin)

# Save the chain
save(output, file = 'chains/spikeslab.dat')
```

```{r}
# Load chains
load('chains/spikeslab.dat')

# Look at the structure of the output is an mcmc object of the library coda
summary(output)
```

```{r}
plot(output)
```

```{r}
autocorr.plot(output)
```

```{r}
pdf(file="spikeslab.pdf")
par(mfrow = c(2, 2))
plot(output, auto.layout = FALSE)
autocorr.plot(output)
dev.off()
```
Covariates inclusion analysis using the **Median Probability Model** (MPM) technique: pick variables with estimated posterior inclusion probabilities higher than $0.5$
```{r}
# We save the posterior chain of the inclusion variable in post_g
post_g <- as.matrix(output[,13:23])
apply(post_g, 2, "mean")
post_mean_g <- apply(post_g, 2, "mean") 
```
```{r}
# Plot
df <- data.frame(value = post_mean_g, var = colnames(X))
p1 <- ggplot(data = df, aes(y = value, x = var, fill = var)) + 
  geom_bar(stat="identity") + 
  geom_hline(mapping = aes(yintercept = .5), col = 2, lwd = 1.1) +
  coord_flip() + theme_minimal() + theme(legend.position="none") + 
  ylab("Posterior Inclusion Probabilities") + xlab("")
p1
```
```{r}
# Select best model according to MPM
mp_SpSl <- as.vector(which(post_mean_g > 0.5))
post_mean_g[mp_SpSl]
# Plot the mdl chain
plot(output[,"mdl"], pch = 20, xlab = "Iteration", ylab = "Model")
```
Covariates inclusion analysis using the **Another way to choose the model** technique: the Highest Posterior Density model (HPD) pick a model with the highest estimated posterior probability.
```{r}
# Number of models visited
length(unique( output[,"mdl"]))
```
```{r}
# Post frequency of visited models
visited_models <- sort(table(output[,"mdl"]), decreasing = TRUE)
barplot(visited_models, xlab = "N° Model", ylab = "Posterior Frequency")
```
```{r}
# Getting the unique profiles and sort the results
unique_model <- unique(post_g, MARGIN = 1)
freq <- apply(unique_model, 1,
              function(b) sum(apply(post_g, MARGIN = 1, function(a) all(a == b))))
cbind(unique_model[order(freq,decreasing = T),], sort(freq,decreasing = T))
```
```{r}
# Select the HPD model 
colnames(X)[as.logical(unique_model[which.max(freq),])]
HDP_SpSl <- c(1:12)[as.logical(unique_model[which.max(freq),])]
```

